Breeding bird indicators

### 2023-11-14 trophic_levels-biomass_indicators.rmd
add figure for repport and update methods

The herbivore data is an extension of the data presented in [Austrheim et al. (2008)](https://doi.org/10.2981/10-038) and [Speed et al. (2015)](https://doi.org/10.1371/journal.pone.0217166). For the development of the trophic interaction indicators the same methods were applied to herbivore data going back to 1907 (contra 1949 in the two studies above). This data was extracted by Gunnar Austrheim (livestock) and Erling J. Solberg (wild cervids). In each dataset, the metabolic biomass and the raw biomass of a given species is provided for each year and municipality. The 2007 municipalities were used. The data were rasterized to the same grid as the NPP data.

@@

>>>>

The herbivore data is an extension of the data presented in [Austrheim et al. (2008)](https://doi.org/10.2981/10-038) and [Speed et al. (2015)](https://doi.org/10.1371/journal.pone.0217166). For the development of the trophic interaction indicators the same methods were applied to herbivore data going back to 1907 (contra 1949 in the two studies above). This data was extracted by Gunnar Austrheim (livestock) and Erling J. Solberg (wild cervids). In each dataset, the metabolic biomass and the raw biomass of a given species is provided for each year and municipality. The 2007 municipalities were used. The data were rasterized to the same grid as the NPP data.
The livestock biomass is adjusted to account for only the time of year that the animals is outside in nature.

@@

```{r figure-for-rapport, eval=FALSE, include=F}

ggplot()+geom_sf(data=norcounty,fill="white",lwd=0.1)+
  geom_spatraster(data=diffcarn[[c(1,12)]])+
  ggtitle('Difference from expected carnivore biomass')+
  scale_fill_distiller(type="div",limit=c(-100,100),oob=squish,na.value=NA,"% difference from \nexpected biomass")+
  facet_wrap(~lyr)+
  theme_bw()
ggsave("images/expCarnivoreBiomass.jpg")
```
